Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-09-16 main.tex
major update

\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
% \usepackage{fullpage}
\input{header}

@@

% Exterior calculus % DONE: MV recommends moving this down to finish the current line of thoughts 
\todo{Where to place this paragraph?}
Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus~\cite{greub1967multilinear,lee2012smooth}. Exterior calculus is used ubiquitously in the mathematical literature of physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite,gross2004electromagnetic,arnold2006finite,arnold2009geometric,arnold2010finite,demlow2014posteriori,licht2021local,arnold2021complexes}. Loosely speaking, exterior calculus is the calculus of antisymmetric tensor fields. The formalism is independent of the dimension and highlights underlying geometric structures common to the gradient, curl, and divergence operators.
%It also enables us to leverage on the rich literature of Sobolev spaces of differential forms.
For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
% DONE: Theo : paragraph feels misplaced 
\\

@@

We shift gears and move from a combinatorial study of triangulations to an analytical study:
we introduce quantitative measures for the geometric quality of triangulations. 
These indicate of the regularity of simplex shapes. 
Most of such \emph{shape measures} in the literature are based on geometric features, 
but it will also be helpful to use indicators based on affine transformations associated with the mesh. %;this is because the properties of these transformations are what shows up in our estimates.

@@

Whenever $T$ is any $n$-dimensional simplex $T$,
we define the \textit{geometric shape measure} $\kappa(T)$
and the \textit{algebraic shape measure} $\alpha(T)$ by 
\begin{align}\label{math:shapemeasure}
    \kappa(T)
    := 
    \frac{ \diam(T)^{n} }{ n! \vol(T) }
    ,
    \qquad 
    \alpha(T)
    := 
    \sup_{ \varphi : \Delta^n \rightarrow T } 
    \frac{ \sigma_{\max}( \Jacobian \varphi ) }{ \sigma_{\min}( \Jacobian \varphi ) }
    ,
\end{align}
where the last suprenum is taken over all affine transformation from the reference $n$-simplex onto the $n$-simplex $T$. 
% DONE: Although this is fairly clear upon reading, we could specify in word that $\kappa(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\rho(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
Moreover, when $\calT$ is an $n$-dimensional simplicial complex, we naturally introduce 
\begin{align}\label{math:shapemeasure:triangulation}
    \kappa(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa(T),
    \quad 
    \alpha(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \alpha(T).
\end{align}
Here, $\kappa(\calT)$ and $\alpha(\calT)$ are the geometric and algebraic shape measures of the triangulation.

\begin{lemma}\label{lemma:affinetransform}
    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
    \begin{gather*}
        \| \Jacobian \varphi \|
        \leq 
        \Ceins{n} \cdot \diam(T) % DONE: can this improved?
        ,
        \qquad 
        \| \Jacobian \varphi^{-1} \|
        \leq 
        \Czwei{n} \cdot 
        \kappa(T) 
        \diam(T)^{-1}
        ,
        \\
        \alpha(T)
        \leq 
        \Cdrei{n}
        % \sqrt{ \frac{n}{ (n-1)^{n-1} } }
        \kappa(T)
        .
    \end{gather*}
    Here,
    \begin{align*}
        \Ceins{n} \leq \sqrt{n},
        \quad 
        \Czwei{n} \leq          \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}, 
        \quad 
        \Cdrei{n} \leq \sqrt{n} \left( \frac{n}{n-1} \right)^{\frac{n-1}{2}}
        . 
    \end{align*}
\end{lemma}
\begin{proof}
    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of the Jacobian $\Jacobian\varphi$ in descending order.
    The Jacobian determinant is the product of these singular values. 
    By a result of Hong and Pan \cite{hong1992lower},
    \begin{align*}
        \sigma_{n}
        &\geq 
        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
        \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n-1} }
        = 
        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
        \frac{ n! \vol(T) }{ \diam(T)^{n-1} }
        .
    \end{align*}
%     To get the second inequality, we multiple the last term by $\sigma_{1} / ( \sqrt{n} \diam(T) ) \leq 1$.
    The second inequality follows. 
    To get the third inequality, we divide both sides by $\sigma_{1}$ and use $\sigma_{1} \leq \sqrt{n} \diam(T)$.

%     By a result of Yu and Gu \cite{yisheng1997note},
%     \begin{align*}
%         \frac{ \sigma_{n} }{ \sigma_{1} }
%         &\geq 
%         \det(\Jacobian\varphi)
%         \left( \frac{n-1}{\|\Jacobian\varphi\|_{F}^{2}} \right)^{\frac{n-1}{2}}
%         \sigma_{1}^{-1}
%         \geq 
%         \left( \frac{n-1}{n^{2}} \right)^{\frac{n-1}{2}}
%         \det(\Jacobian\varphi)
%         \left( \frac{1}{ \diam(T)^{n-1} } \right)^{}
%         \frac{1}{\sqrt{n} \diam(T)}
%         \\&
%         \geq 
%         \left( \frac{n-1}{n^{2}} \right)^{\frac{n-1}{2}}
%         \frac{1}{\sqrt{n}}
%         \frac{ n! \vol(T) }{ \diam(T)^{n} }
%         .
%     \end{align*}
%     Since $\diam(T) \leq \sqrt{2} \sigma_{1}$, the desired result follows. % THIS IS OPTIMAL
%     Thus, $\sigma_1/\sigma_n \leq \sigma_1^{n} / { \det(\Jacobian\varphi) }$ and 
%     \begin{gather*}
%         \diam(T) 
%         \leq 
%         \sqrt{2} \sigma_1 
%         \leq 
%         \sqrt{2} 
%         \frac{ \sigma_1^{n} }{ { \det(\Jacobian\varphi) } } 
%         \sigma_n
%         \leq 
%         \sqrt{2n^{n}} 
%         \left( \frac{ \diam(T)^{n} }{ n! \vol(T) } \right)
%         \sigma_n
%         .
%     \end{gather*}
%     The desired result is thus evident. 
\end{proof}

@@

\begin{proof}
    Let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
    By the volume formula for simplices, $\vol(T_1) = h_1 \vol(F)/n$ and $\vol(T_2) = h_2 \vol(F)/n$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$.
    The diameter of $F$ is at least as large as the height $h_S$ of some other facet $S$ of $T$. Recursive application of the volume formula shows 
    \begin{align*}
        \vol(T) = \frac{1}{n!} h_S h_2 \cdots h_n,
    \end{align*}
    where $h_S \leq \diam(F)$ and $h_2, \cdots, h_n \leq \diam(T)$. Now, 
    \begin{align*}
        \diam(T) \frac{ n! \vol(T) }{ \diam(T)^{n} } \leq h_S \leq \diam(F).
    \end{align*}
    The first estimate follows. 
    On the other hand, 
    \begin{align*}
        h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n \cdot \vol(T_1)} \diam(F),
        \\
        h_2 &= n \frac{\vol(T_2)}{\vol(F)} \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
        .
    \end{align*}
    The second estimate follows. 
    Lastly, letting $\Xi : T_1 \rightarrow T_2$ be as above, Lemma~\ref{lemma:affinetransform} and the first estimate imply 
    \begin{align*}
        \| \Jacobian \Xi \|
        &
        \leq 
        \Ceins{n}
        \Czwei{n}
        \kappa(T_2)
        \diam(T_1)
        \diam(T_2)^{-1}
        \\&
        \leq 
        \Ceins{n}
        \Czwei{n}
        \kappa(T_2)
        \kappa(T_1) 
        \diam(F)
        \diam(T_2)^{-1}
        \leq 
        \Ceins{n}
        \Czwei{n}
        \kappa(T_2)
        \kappa(T_1) 
        .
    \end{align*}
    All the desired results thus follow.

@@

    u_{\Omega} := |\Omega|^{-1} \int_{\Omega} u(x) \;dx.

@@

    \int_{\Omega} \left( |\Omega|^{-1} \int_{\Omega} |u(x)| \;dx \right)^{p}
    \int_{\Omega} |\Omega|^{-1} \int_{\Omega} |u(x)|^{p} \;dx

@@

 We assess the norm of this potential. We observe 
 \begin{gather*}
    \| w'_{F_m} \|_{L^{p}(T_m)}
    \leq 
    \| u_{F_m} \|_{L^{p}(T_m)}
    +
    \| c_{m} \|_{L^{p}(T_m)},
    \\
    \| c_{m} \|_{L^{p}(T_m)}
    = 
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
    \| c_{m} \|_{L^{p}(T_{{m-1}})},
    \\ 
    \| c_{m} \|_{L^{p}(T_{{m-1}})}
    \leq 
    \| w_{m-1}\|_{L^{p}(T_{{m-1}})} + \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})} 
    .
 \end{gather*}
 In particular,
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}
    &
    \leq 
    \| u_{F_m} \|_{L^{p}(T_m)}
    \\&\qquad 
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
    \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})}
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
    .
 \end{align*}
 We sum the two integrals of $u_{F_m}$. 
 % 
 In the special case $p=1$,
 \begin{align*}
    \| w_{m} \|_{L^{1}(T_m)}
    \leq 
    \max\left(
        1, \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) } 
    \right)
    \| u_{F_m} \|_{L^{1}(U_{F_m})}
    +
    \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) }
    \| w_{m-1}\|_{L^{1}(T_{{m-1}})}
    .
 \end{align*}
 In the special case $p=\infty$, 
 \begin{align*}
    \| w_{m} \|_{L^{\infty}(T_m)}
    \leq 
    2
    \| u_{F_m} \|_{L^{\infty}(U_{F_m})}
    +
    \| w_{m-1}\|_{L^{\infty}(T_{{m-1}})}
    .
 \end{align*}
 % 1/q = 1 - 1/p = (p-1)/p 
 When $1 < p < \infty$, letting $q := p/(p-1) \in [1,\infty]$ be the complementary exponent, we observe 
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}
    &\leq 
    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
    \left( 
        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
        +
        \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})}^{p}
    \right)^{\frac 1 p}
    \\&\qquad 
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
    \\&\leq 
    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
    \| u_{F_m} \|_{L^{p}(U_{F_m})} 
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
    .
 \end{align*}
 Recursive application provides the following estimate:
%  if $T_0 = S_0, S_1, \dots, S_m = T_m$ is a sequence of $n$-simplices in $\calT$
%  such that \color{red}$S_{t-1}$ precedes $S_{t}$ in the graph \color{black} and such that $F_t = S_t \cap S_{t-1}$,
%  then 
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}
    &\leq 
    \sum_{t=1}^{m} 
    \left( 
        \prod_{t < l \leq m} 
        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
    \right)
    \left( 1 + \frac{ \vol(T_t)^{\frac q p} }{ \vol(T_{t-1})^{\frac q p} } \right)^{\frac 1 q}
    \| u_{F_t} \|_{L^{p}(U_{F_t})}
    \\&\quad \quad \quad 
    +
    \left( 
        \prod_{0 < l \leq m} 
        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
    \right)
    \| u_{T_0}\|_{L^{p}(T_{0})}
    .
 \end{align*}
 Taking into account Definition~\eqref{math:todo}, we obtain the desired inequality.
%  \begin{align*}
%     \| w_{m} \|_{L^{p}(T_m)}^{p}
%     &\leq 
%     (m+1)^{p-1}
%     % \sum_{t=1}^{m} \rho(\calT)^{m-t} 
%     % \sum_{t=0}^{m-1} \rho(\calT)^{t} 
%     \frac{\rho(\calT)^{m}-1}{\rho(\calT)-1}
%     \left( 1 + \rho(\calT)^{\frac q p} \right)^{p/q}
%     \| u_{F_t} \|_{L^{p}(U_{F_t})}^{p}
%     \\&\quad \quad \quad 
%     +
%     (m+1)^{p-1}
%     \rho(\calT)^{m-1}
%     \| u_{T_0}\|_{L^{p}(T_{0})}^{p}
%     .
%  \end{align*}
%  Notice that $p/q = p - 1$.
 % 
 Repeating this argument produces $w \in L^{p}(\Omega)$ 
 such that for all $n$-simplices $T \in \calT$ we have the restriction $w_{|T} \in W^{1,p}(T)$ with $w_{|T} = u + c_{0}$.
 In particular, $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$.
\end{proof}

@@

We begin with introducing the Costabel-McIntosh kernel.
For any $\ell \in \{0,\dotsc,n\}$, we define the kernel $G_{\ell} : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
\begin{equation}\label{math:mainkernel}
  G_{\ell}(x,y) = \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} |\Omega|^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt
  .
\end{equation}
Given a differential form $u \in {C^\infty_c}(\bbR^n,\Alt^\ell)$, where \(1 \leq \ell \leq n\), 
we then define the integral operators
\begin{align*}
  \Poinc_{\ell} u(x) &= \int_{\Omega} G_{n-\ell+1}(y,x) \,(x-y)\lrcorner u(y)\,dy,
  \\
  \Bogov_{\ell} u(x) &= \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy.
\end{align*}
We call $\Poinc_{\ell}$ the Poincar\'e operator and $\Bogov_{\ell}$ the Bogovski\u{\i} operator. 
\\

>>>>

\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\input{header}

@@

% Exterior calculus % DONE: MV recommends moving this down to finish the current line of thoughts 
\todo{What is the best place for this paragraph?}
Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus~\cite{greub1967multilinear,lee2012smooth}. Exterior calculus is used ubiquitously in the mathematical literature of physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite,gross2004electromagnetic,arnold2006finite,arnold2009geometric,arnold2010finite,demlow2014posteriori,licht2021local,arnold2021complexes}. Loosely speaking, exterior calculus is the calculus of antisymmetric tensor fields. The formalism is independent of the dimension and highlights underlying geometric structures common to the gradient, curl, and divergence operators.
%It also enables us to leverage on the rich literature of Sobolev spaces of differential forms.
For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
% DONE: Theo : paragraph feels misplaced 
\\

@@

We shift gears and move from a combinatorial study of triangulations to an analytical study:
we introduce quantitative measures for the geometric quality of triangulations. 
These indicate of the regularity of simplex shapes. 
Most of such \emph{shape measures} in the literature are based on geometric features, 
but it will also be helpful to use indicators based on affine transformations associated with the mesh. %;this is because the properties of these transformations are what shows up in our estimates. 
All these quantities have in common that they can be computed from purely local information. 
While there are many equivalent shape measures, we use the ones that most immediate appear in our proofs.

\todo{MWL: The different geometric quantities in this section should really be just what is needed later. Any shape measure should be locally measurable and close to what appears in the right-hand sides of the main results. Any inequalities here should be as tight as possible. }

We write $\diam(T)$ and $\vol(T)$ for the diameter and $n$-dimensional volume of any $n$-simplex $T$.
Moreover, $\height(T)$ refers to the smallest height of any of the vertices of the simplex $T$.

@@

Given a matrix $A \in \bbR^{n \times n}$, we let $\sigma_{1}(A) \geq \dots \geq \sigma_{n}(A) \geq 0$ denote the descending sequence of its singular values, 
where $\sigma_{\max}(A) := \sigma_{1}(A)$ is the largest and $\sigma_{\min}(A) := \sigma_{n}(A)$ is the smallest. 
We recall that the $\ell^{2}$ operator norm of $\|A\|_{2}$ agrees with $\sigma_{\max}(A)$,
and if $A$ is invertible, then $\|A^{-1}\| = \sigma_{\min}(A)^{-1}$.
% Another norm on matrices, less common but useful for us, is the \emph{maximum column norm} $\|A\|_{\maxcol}$, which is defined as the largest $\ell^{2}$-norm of any column of $A$.

Whenever $T$ is any $n$-dimensional simplex $T$,
we define the \textit{geometric shape measure} $\kappa(T)$,
the \textit{algebraic shape measure} $\kappa_{2}(T)$,
and the \textit{aspect shape measure} $\kappa_{\maxcol}(T)$ 
by 
\begin{align}\label{math:shapemeasure}
    \kappa(T)
    := 
    \frac{ \diam(T)^{n} }{ n! \vol(T) }
    ,
    \qquad 
    \kappa_{\maxcol}(T)
    := 
    \frac{ \diam(T) }{ \height(T) }
    ,
    \qquad 
    \kappa_{2}(T)
    := 
    \sup_{ \varphi : \Delta^n \rightarrow T } 
    \frac{ \sigma_{\max}( \Jacobian \varphi ) }{ \sigma_{\min}( \Jacobian \varphi ) }
%     \sup_{ \varphi : \Delta^n \rightarrow T } \| \Jacobian \varphi \|_{\maxcol} \| \Jacobian \varphi^{-1} \|_{\maxcol}
    ,
\end{align}
where the last supremum is taken over all affine transformation from the reference $n$-simplex onto the $n$-simplex $T$. 
% DONE: Although this is fairly clear upon reading, we could specify in word that $\kappa(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\rho(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.

When $\calT$ is an $n$-dimensional simplicial complex, we naturally introduce 
\begin{align}\label{math:shapemeasure:triangulation}
    \kappa(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa(T)
    ,
    \quad 
    \kappa_{\maxcol}(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa_{\maxcol}(T)
    ,
    \quad 
    \kappa_{2}(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa_{2}(T)
    .
\end{align}
We call these the geometric, algebraic, and aspect shape measure, respectively, of the triangulation.

We gather a few relationships between geometric and algebraic entities and compare the different shape measures.

\begin{lemma}\label{lemma:measurerelationships}
    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
    \begin{gather*}
        \| \Jacobian \varphi \|
        \leq 
        \Ceins{n} \cdot \diam(T) % DONE: can this improved?
        ,
        \qquad 
        \| \Jacobian \varphi^{-1} \|
        \leq 
        \Czwei{n} \cdot 
        \kappa(T) 
        \diam(T)^{-1}
        ,
        \\
        \kappa_{2}(T)
        \leq 
        \Cdrei{n}
        % \sqrt{ \frac{n}{ (n-1)^{n-1} } }
        \kappa(T)
        ,
        \qquad 
        %         \kappa(T)^{\frac 1 n}
        %         \leq 
        \kappa_{\maxcol}(T)
        \leq 
        \kappa(T)
        .
    \end{gather*}
    Here,
    \begin{align*}
        \Ceins{n} \leq \sqrt{n},
        \quad 
        \Czwei{n} \leq          \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}, 
        \quad 
        \Cdrei{n} \leq \Ceins{n}\Czwei{n} %\sqrt{n} \left( \frac{n}{n-1} \right)^{\frac{n-1}{2}}
        . 
    \end{align*}
\end{lemma}
\begin{proof}
%     The columns of the matrix $\Jacobian \varphi^{-1}$ are the gradients of the barycentric coordinates of the vertices of $T$,
%     except for the vertex $\varphi(0)$. It immediately follows that 
%     \begin{align*}
%         \| \Jacobian \varphi^{-1} \|_{2} \leq \sqrt{n} \cdot \height(T)^{-1}
%         .
%     \end{align*}
%     The smallest height in the reference simplex $\Delta^{n}$ is $1/\sqrt{n}$. 
%     
    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of the Jacobian $\Jacobian\varphi$ in descending order.
    The Jacobian determinant is the product of these singular values. 
    By a result of Hong and Pan \cite{hong1992lower},
    \begin{align*}
        \sigma_{n}
        &\geq 
        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
        \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n-1} }
        = 
        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
        \frac{ n! \vol(T) }{ \diam(T)^{n-1} }
        .
    \end{align*}
%     To get the second inequality, we multiple the last term by $\sigma_{1} / ( \sqrt{n} \diam(T) ) \leq 1$.
    The second inequality follows by taking the reciprocal. 
    The definition of the condition number now gives the third inequalities. 
    % To get the third inequality, we divide both sides by $\sigma_{1}$ and use $\sigma_{1} \leq \sqrt{n} \diam(T)$.
    Finally, 
    if $F$ is the face of $T$ opposite to the vertex with the smallest height, then 
    \begin{align*}
        \frac{ \diam(T) }{ \height(T) }
        \leq 
        \frac{ \diam(T) \vol(F) }{ n \vol(T) }
        \leq 
        \frac{ \diam(T)^{n} }{ n! \vol(T) }
        .
    \end{align*}
%     Since $n! \vol(T)$ is bounded from below by the product of any $n$ different heights of $T$, it follows that 
%     \begin{align*}
%         \frac{ \diam(T)^{n} }{ n! \vol(T) }
%         \leq 
%         \frac{ \diam(T)^{n} }{ \height(T)^{n} }
%         .
%     \end{align*}
    That shows the fourth and last of the inequalities. 
\end{proof}

@@

\begin{proof}
    Let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
    By the volume formula for simplices, $\vol(T_1) = h_1 \vol(F)/n$ and $\vol(T_2) = h_2 \vol(F)/n$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$.
    The diameter of $F$ is at least as large as the height $h_S$ of some other facet $S$ of $T$. Recursive application of the volume formula shows 
    \begin{align*}
        \vol(T) = \frac{1}{n!} h_S h_2 \cdots h_n,
    \end{align*}
    where $h_S \leq \diam(F)$ and $h_2, \cdots, h_n \leq \diam(T)$. Now, 
    \begin{align*}
        \diam(T) \frac{ n! \vol(T) }{ \diam(T)^{n} } \leq h_S \leq \diam(F).
    \end{align*}
    The first estimate follows. 
    On the other hand, 
    \begin{align*}
        h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n \cdot \vol(T_1)} \diam(F),
        \\
        h_2 &= n \frac{\vol(T_2)}{\vol(F)} \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
        .
    \end{align*}
    The second estimate follows. 
    Lastly, letting $\Xi : T_1 \rightarrow T_2$ be as above, Lemma~\ref{lemma:measurerelationships} and the first estimate imply 
    \begin{align*}
        \| \Jacobian \Xi \|
        &
        \leq 
        \Ceins{n}
        \Czwei{n}
        \kappa(T_2)
        \diam(T_1)
        \diam(T_2)^{-1}
        \\&
        \leq 
        \Ceins{n}
        \Czwei{n}
        \kappa(T_2)
        \kappa(T_1) 
        \diam(F)
        \diam(T_2)^{-1}
        \leq 
        \Ceins{n}
        \Czwei{n}
        \kappa(T_2)
        \kappa(T_1) 
        .
    \end{align*}
    All the desired results thus follow.

@@

    u_{\Omega} := \vol(\Omega)^{-1} \int_{\Omega} u(x) \;dx.

@@

    \int_{\Omega} \left( \vol(\Omega)^{-1} \int_{\Omega} |u(x)| \;dx \right)^{p}
    \int_{\Omega} \vol(\Omega)^{-1} \int_{\Omega} |u(x)|^{p} \;dx

@@

 We assess the norm of this potential. We observe 
 \begin{gather*}
    \| w'_{F_m} \|_{L^{p}(T_m)}
    \leq 
    \| u_{F_m} \|_{L^{p}(T_m)}
    +
    \| c_{m} \|_{L^{p}(T_m)},
    \\
    \| c_{m} \|_{L^{p}(T_m)}
    = 
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
    \| c_{m} \|_{L^{p}(T_{{m-1}})},
    \\ 
    \| c_{m} \|_{L^{p}(T_{{m-1}})}
    \leq 
    \| w_{m-1}\|_{L^{p}(T_{{m-1}})} + \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})} 
    .
 \end{gather*}
 In particular,
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}
    &
    \leq 
    \| u_{F_m} \|_{L^{p}(T_m)}
    \\&\qquad 
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
    \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})}
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
    .
 \end{align*}
 We sum the two integrals of $u_{F_m}$. 
 % 
 In the special case $p=1$,
 \begin{align*}
    \| w_{m} \|_{L^{1}(T_m)}
    \leq 
    \max\left(
        1, \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) } 
    \right)
    \| u_{F_m} \|_{L^{1}(U_{F_m})}
    +
    \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) }
    \| w_{m-1}\|_{L^{1}(T_{{m-1}})}
    .
 \end{align*}
 In the special case $p=\infty$, 
 \begin{align*}
    \| w_{m} \|_{L^{\infty}(T_m)}
    \leq 
    2
    \| u_{F_m} \|_{L^{\infty}(U_{F_m})}
    +
    \| w_{m-1}\|_{L^{\infty}(T_{{m-1}})}
    .
 \end{align*}
 % 1/q = 1 - 1/p = (p-1)/p 
 When $1 < p < \infty$, letting $q := p/(p-1) \in [1,\infty]$ be the complementary exponent, we observe 
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}
    &\leq 
    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
    \left( 
        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
        +
        \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})}^{p}
    \right)^{\frac 1 p}
    \\&\qquad 
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
    \\&\leq 
    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
    \| u_{F_m} \|_{L^{p}(U_{F_m})} 
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
    .
 \end{align*}
 Recursive application provides the following estimate:
%  if $T_0 = S_0, S_1, \dots, S_m = T_m$ is a sequence of $n$-simplices in $\calT$
%  such that \color{red}$S_{t-1}$ precedes $S_{t}$ in the graph \color{black} and such that $F_t = S_t \cap S_{t-1}$,
%  then 
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}
    &\leq 
    \sum_{t=1}^{m} 
    \left( 
        \prod_{t < l \leq m} 
        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
    \right)
    \left( 1 + \frac{ \vol(T_t)^{\frac q p} }{ \vol(T_{t-1})^{\frac q p} } \right)^{\frac 1 q}
    \| u_{F_t} \|_{L^{p}(U_{F_t})}
    \\&\quad \quad \quad 
    +
    \left( 
        \prod_{0 < l \leq m} 
        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
    \right)
    \| u_{T_0}\|_{L^{p}(T_{0})}
    .
 \end{align*}
 % Taking into account Definition~\eqref{math:todo}, we obtain the desired inequality. % TODO: what was originally used here?
 We obtain the desired estimate. 
%  \begin{align*}
%     \| w_{m} \|_{L^{p}(T_m)}^{p}
%     &\leq 
%     (m+1)^{p-1}
%     % \sum_{t=1}^{m} \rho(\calT)^{m-t} 
%     % \sum_{t=0}^{m-1} \rho(\calT)^{t} 
%     \frac{\rho(\calT)^{m}-1}{\rho(\calT)-1}
%     \left( 1 + \rho(\calT)^{\frac q p} \right)^{p/q}
%     \| u_{F_t} \|_{L^{p}(U_{F_t})}^{p}
%     \\&\quad \quad \quad 
%     +
%     (m+1)^{p-1}
%     \rho(\calT)^{m-1}
%     \| u_{T_0}\|_{L^{p}(T_{0})}^{p}
%     .
%  \end{align*}
%  Notice that $p/q = p - 1$.
 % 
 Repeating this argument produces $w \in L^{p}(\Omega)$ 
 such that for all $n$-simplices $T \in \calT$ we have the restriction $w_{|T} \in W^{1,p}(T)$ with $w_{|T} = u + c_{0}$.
 In particular, $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$.
\end{proof}

@@

We begin with introducing the Costabel-McIntosh kernel.
For any $\ell \in \{0,\dotsc,n\}$, we define the kernel $G_{\ell} : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
\begin{equation}\label{math:mainkernel}
  G_{\ell}(x,y) = \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} \vol(\Omega)^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt
  .
\end{equation}
Given a differential form $u \in {C^\infty_c}(\bbR^n,\Alt^\ell)$, where \(1 \leq \ell \leq n\), 
we then define the integral operators
\begin{align*}
  \Poinc_{\ell} u(x) &= \int_{\Omega} G_{n-\ell+1}(y,x) \,(x-y)\lrcorner u(y)\,dy,
  \\
  \Bogov_{\ell} u(x) &= \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy.
\end{align*}
We call $\Poinc_{\ell}$ the Poincar\'e operator and $\Bogov_{\ell}$ the Bogovski\u{\i} operator. 
\\
